\section{STAKEHOLDER REQUIREMENTS}

The following requirements represent the needs and expectations of all stakeholders, including
drone pilots, system operators, project sponsors, safety personnel, and integration engineers. 
These requirements describe \emph{what} the system must achieve from a user and stakeholder 
perspective, without specifying technical implementation details.

\begin{enumerate}

    % --------------------------------------------------
    % Core Functionality
    % --------------------------------------------------
    \item \textbf{Live Video Transmission:} \\
          The system shall transmit a real-time digital video feed from the drone-mounted camera 
          to the pilot’s ground display (FPV goggles or HDMI monitor) with minimal noticeable delay.

    % --------------------------------------------------
    % Transmission Mode Flexibility
    % --------------------------------------------------
    \item \textbf{Selectable Transmission Modes:} \\
          The user shall be able to select between:
          \begin{itemize}
              \item \textbf{Low-Latency Mode} (unconfirmed packets for racing/fast response)
              \item \textbf{High-Quality Mode} (confirmed packet retransmission for improved clarity)
          \end{itemize}
          The mode selection shall be intuitive and accessible through the ground station interface.

    % --------------------------------------------------
    % Reliability and Connection Recovery
    % --------------------------------------------------
    \item \textbf{Automatic Link Recovery:} \\
          The system shall automatically detect, handle, and recover from temporary signal loss 
          without requiring user intervention. Video connection shall re-establish as soon as RF 
          conditions permit.

    % --------------------------------------------------
    % Ease of Use
    % --------------------------------------------------
    \item \textbf{User-Friendly Operation:} \\
          The system shall be easy to install, configure, and operate for a first-time FPV pilot. 
          Basic setup (connection, channel selection, and display output) shall require minimal steps 
          and shall not require specialized technical knowledge.

    % --------------------------------------------------
    % Physical Robustness
    % --------------------------------------------------
    \item \textbf{Environmental and Mechanical Durability:} \\
          The drone-mounted module shall be capable of withstanding:
          \begin{itemize}
              \item Typical drone vibration during flight  
              \item Light to moderate impacts from crashes  
              \item Normal outdoor operating conditions (sunlight, temperature variations, dust exposure)
          \end{itemize}
          without degradation of performance.

    % --------------------------------------------------
    % Compatibility
    % --------------------------------------------------
    \item \textbf{Flight Controller Integration:} \\
          The system shall be compatible with commonly used FPV drone flight controllers and firmware 
          such as Betaflight. It shall support remote configuration, telemetry exchange, and 
          communication with onboard systems.

    % --------------------------------------------------
    % Safety Expectations
    % --------------------------------------------------
    \item \textbf{Safe Operation:} \\
          The system shall operate within regulatory RF limits and shall not interfere with 
          flight-critical electronics on the aircraft.

\end{enumerate}
